QPLIB: A Library of Quadratic Programming Instances

### 2017-01-20 QPLIB-2.3.tex
lindo = lindoglobal = lindo api, lgo_bb is not a complete solver
- deja vu

The solvers in Table \ref{t:solvers} BB type methods are:
%
\begin{itemize}
 \item {\sc Antigone}, {\sc Baron}, {\sc Couenne}, {\sc Lindo}, {\sc LindoGlobal}, {\sc SCIP}, {\sc lgo\_bb}, which implement complete BB algorithms for QGQ;
 %
\item {\sc CPLEX}, which implements a complete BB algorithm for QGL;
%
 \item {\sc Knitro\_bb}, {\sc BonMin}, {\sc sBB}, {\sc Xpress}, {\sc Gurobi}, and {\sc Mosek} which implement complete BB algorithms for CGC.
\end{itemize}
%
We remark that the latter category can be used as incomplete solvers for QGQ. We also remark that CPLEX can currently only target problems with linear constraints when the objective function is nonconvex \cite{bliek}.

>>>>

The solvers in Table \ref{t:solvers} BB type methods are:
%
\begin{itemize}
 \item {\sc Antigone}, {\sc Baron}, {\sc Couenne}, {\sc Lindo API}, {\sc SCIP}, which implement complete BB algorithms for QGQ;
 %
\item {\sc CPLEX}, which implements a complete BB algorithm for QGL;
%
 \item {\sc Knitro\_bb}, {\sc BonMin}, {\sc sBB}, {\sc Xpress}, {\sc Gurobi}, and {\sc Mosek} which implement complete BB algorithms for CGC.
\end{itemize}
%
We remark that the latter category can be used as incomplete solvers for QGQ. We also remark that CPLEX can currently only target problems with linear constraints when the objective function is nonconvex \cite{bliek}.

\todo[inline]{{\sc lgo\_bb} was in the listing above, but is it a complete solver for any class?}
